Playing against Nature: causal discovery for decision making under uncertainty

### 2018-05-18 Segundo_Semestre/CausalML_Workshop/Paper_long_version.tex
comentarios caso3

>>>>

As in the previous case, consider a repeated game where the base game consists of Nature assigning a disease to a patient, a medic choosing a treatment for it and Nature once again choosing the final outcome. This final choice of Nature is governed by the causal model.

In this game, as well as in the previous one, the decision maker will attempt to learn by updating, and using, beliefs in a suitable way.

The most notable difference with the previous case is that the \textit{structure} of the model is also to be learned in such a way that both the structure and parameters converge to the true model in the limit.
